### 2015-06-07 Paper_english/abstract.tex
correcciones abstract, introduccion

\begin{abstract}
%\boldmath
This paper proposes an optical motion capture system based on markers that facilitates biomechanical motion people analysis.
The system consists of separate blocks, giving an overall solution which allows to easily modify or replace components.
Guidelines are described for generating a virtual laboratory from which to obtain a database with sequences of synthetic videos and are explored the characteristics required of a laboratory based on optical capture markers to facilitate processing.
A set of metrics is presented to measure the performance of each block and the overall system.
Tests on the software implemented reflected that it has an accuracy of centimeter on sequences obtained in controlled environments. These results are good considering that the algorithms used in each block are of low complexity and can be optimized.
\keywords{
	Biomechanic, calibration, segmentation, reconstruction, tracking, virtual laboratory.
}
\end{abstract}

>>>>

\begin{abstract}
%\boldmath
This paper proposes an optical motion capture system based on markers that facilitates biomechanical analysis from people movements.
The system consists of separate blocks, giving an overall solution which allows to easily modify or replace components.
Guidelines are described for generating a virtual laboratory from which to obtain a database with sequences of synthetic videos and are explored the characteristics required of a laboratory based on optical capture markers to facilitate processing.
A set of metrics is presented to measure the performance of each block and the overall system.
Tests on the software implemented reflected that it has an accuracy in the order of centimeters on sequences obtained in controlled environments. These results are acceptables considering that the algorithms used in each block are of low complexity and can be optimized.
\keywords{
	Biomechanic, calibration, segmentation, reconstruction, tracking, virtual laboratory.
}
\end{abstract}

### 2015-06-07 Paper_english/introduccion.tex
correcciones abstract, introduccion

The Video analysis is a critical tool for data collection and study. Tracking reference points are used for the position calculation and other associated variables such as speed, acceleration and hence movement.
The manual tracking of those points can be tedious so it is necessary to have a tool to perform this task automatically. 
Some examples that illustrate these needs are in \emph{health care level} in the area of \emph{physiotherapy}, \emph{biomechanics academic research},
\emph{measures of performance} in top-level sport and the \emph{3D animation}, among others.
The examples above defined use cases with different characteristics, so the search for a single solution covering the particular needs of all of them is complex. Having these tools is critical to the needs of professional teams, whose alternative are high-cost commercial products.\\
\hspace*{0.5cm}This project sought to perform a basic and functional open source application video analysis, to provide solution to the above needs a project basis using existing free software, or failing that, developing a prototype software that covers the entire problem generally, for extending the application to other use cases.\\
\hspace*{0.5cm}The system created aims under certain controlled conditions to obtain the spatial coordinates of a number of interest points on a patient.
Placing the patient with black suit and white markers in an environment with adequate lighting, is filmed with multiple cameras over time, this information is brought to the computer and processed to obtain the 3D trayectories of the markers.\\
\hspace*{0.5cm}Working from the algorithm proposed by Herda \cite{herda}, trying to do reproducible version thereof containing measures performance on each stage,  as well as a methodology for designing a virtual laboratory jointly developing a complete test system.

>>>>

The video analysis is an essential tool for study and data collection. Tracking reference points is used for calculate position and other associated variables such as speed, acceleration and therefore movement.
The manual tracking of those points can be tedious so it is necessary to have a tool to perform this task automatically. 
Some examples that illustrate these needs are: at \emph{health care level} in the area of \emph{physiotherapy}, \emph{biomechanics academic research},
\emph{measures of performance} in professional sports and \emph{3D animation}.
These examples define use cases with different characteristics, so search for a single solution that covers particular needs of all of them is complex. Have these tools is essential to professional teams needs, whose alternative are high-cost commercial products.\\
\hspace*{0.5cm}This project sought to perform a basic and functional open source video analysis application to provide solution to the above needs, either using an existing open source project as starting point, or developing a prototype software that covers the entire problem generally, to extend the application to other use cases.\\
\hspace*{0.5cm}The system created aims, under certain controlled conditions, to obtain the spatial coordinates from a number of points on a patient. To do this the patient, with a black suit and white markers, is placed in an environment with adequate lighting, then is filmed with multiple cameras over time. This information is brought to the computer and processed to obtain the 3D trayectories of the markers.\\
\hspace*{0.5cm}Working from the algorithm proposed by Herda \cite{herda}, it is proposed a reproducible version from it, containing measures performance on each stage, as well as a methodology for designing a virtual laboratory, developing a complete test system.
